### 2025-07-04 paper-reviews/papers-2025.tex
Add AVX512-based Base64 paper

    The article highlights how Intel uses ICC compiler and library optimizations to submit higher SPEC CPU scores. The author emphasizes that it is important to use GCC --- an open sources, harder to manipulate compiler --- to achieve apple to apple comparison of different vendors' processors.
\end{itemize}

>>>>

    The article highlights how Intel uses ICC compiler and library optimizations to submit higher SPEC CPU scores. The author emphasizes that it is important to use GCC --- an open sources, harder to manipulate compiler --- to achieve apple to apple comparison of different vendors' processors.

    \item \cite{Wojciech:Avx512Base64:2019}:

    The paper presents AVX512-based base64 encoding and decoding implementation. The implementation achieves five and seven-fold improvement compared to AVX2-based implementation for decoding and encoding correspondingly. The implementation uses AVX512 BMI instructions in a nice way that allows to decode/encode base64 at speed close to memory copy.
\end{itemize}
